formula1

### 2020-03-11 inst/formula1.Rmd
more work

Each row is a driver and each column (after the first) a venue.  We
see that Hamilton, the first row, came second in Australia, first in
China, second in Bahrain, fourth in Russia, and so on.  In the first
column, we see the result from Australia (AUS) in which Hamilton came
second, Vettel first, Bottas third, and so on.  Notation used also
includes six different classes of no-score such as "Ret" for retired,
"WD" for withdrawn, and so on.  I now use bespoke R function
\code{ordertable2supp()}, that translates data of this type into a
log-likelihood.  The function is similar to, but slightly different
from, the analysis in `eurovision.R`.

@@

mallyears <- maxp(F1_total)
```

>>>>

(in the package this is object `F1_table_2017`).  Each row is a driver
and each column (after the first) a venue.  We see that Hamilton, the
first row, came second in Australia, first in China, second in
Bahrain, fourth in Russia, and so on.  In the first column, we see the
result from Australia (AUS) in which Hamilton came second, Vettel
first, Bottas third, and so on.  Notation used also includes six
different classes of no-score such as "Ret" for retired, "WD" for
withdrawn, and so on.

We can represent this data in a different form using
`wikitable_to_ranktable()`:

```{r}
wikitable_to_ranktable(f2017)
```

Looking at the first column ("c1" is read "came first") we see who
came first at each venue: Vettel in Australia (AUS), Hamilton in China
(CHN), Vettel in Bahrain (BHR), and so on.  I now use bespoke R
function \code{ordertable2supp()}, that translates data of this type
into a log-likelihood.  The function is similar to, but slightly
different from, the analysis in `eurovision.R`.

@@

head(F1_total)
```

So object `F1_total` is a likelihood function for all four years data,
on the assumption of independent observations and in this case driver
strength being independent of year.  We can find the evaluate in the same way:

```{r,findmallyears}
mallyears <- maxp(F1_total)
```
